### 2018-06-29 README.Rmd
some more :package: infrastructure

@@

@@

---

>>>>

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/cboettig/taxald.svg?branch=master)](https://travis-ci.org/cboettig/taxald)
[![Coverage status](https://codecov.io/gh/cboettig/taxald/branch/master/graph/badge.svg)](https://codecov.io/github/cboettig/taxald?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/taxald)](https://cran.r-project.org/package=taxald)

@@

**This package is purley exploratory at this stage!**

Central to `taxald` design is to create a *local* database of all avialable taxonomic authority data that we can query quickly, even when working with tens of thousands of species. The second key feature of `taxald` design is to return queries from each authority using a *consistent* and convenient table structure, facilitating queries that compare, combine, or work across names from multiple authorities.

## Install and initial setup

`taxald` should now be installable.  To get started, try:

```{r eval=FALSE}
devtools::install_github("cboettig/taxald")
```

Before we can use most `taxald` functions, we need to do a one-time installation of the database `taxald` uses for almost all commands.  This can take a while to run, but needs only be done once.  The database is installed on your local harddisk and will persist between R sessions.  Download and install the database

```{r}
library(taxald)

```

@@
